---
title: "Cleaning Lipid Names for Annotation Part 3"
subtitle: ""
excerpt: "This post provides some tips on how to clean lipid names input suited for some current nomenclature tools using R"
date: 2022-04-23
author: "Jeremy Selva"
draft: true
images:
series:
tags:
categories:
output: md_document #needed for flair to work
layout: single-sidebar
bibliography: utils/bibliography.bib
csl: utils/f1000research.csl
editor_options: 
  chunk_output_type: console
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(fig.align = "center")

htmltools::tagList(
  xaringanExtra::use_clipboard(
    button_text = "<i class=\"fa fa-clipboard\"></i> Copy Code",
    success_text = "<i class=\"fa fa-check\" style=\"color: #90BE6D\"></i> Copied!",
  ),
  rmarkdown::html_dependency_font_awesome()
)
```

```{r message=FALSE, include=FALSE}
library("rgoslin")
library("reactable")
library("flair")
library("here")
library("readxl")
library("magrittr")
library("stringr")
library("dplyr")
library("purrr")
library("report")
```

## Introduction

Our last function below is able to remove the [SIM] at the end of the transition name

```{r remove_sim, message=FALSE}

clean_acyl <- function(input_acyl = "DG 32:0 [NL-16:0]") {
  
  # If we have a sum composition labelled as [SIM] at the end,
  # remove it and return the results
  if (isTRUE(stringr::str_detect(string = input_acyl,
                                 pattern = "\\s*\\[SIM\\]\\s*$")))
  {
    input_acyl <- input_acyl %>%
      stringr::str_remove(pattern = "\\s*\\[SIM\\]\\s*$")
    
    return(input_acyl)
  }
  
  return(input_acyl)
}

```

```{r, warning=FALSE, message=FALSE}

clean_acyl("TG 54:3 [SIM]")

```

We continue the cleaning task for these transitions.

| Given Name          | Clean Name For Annotation | Precursor Ion | Product Ion |
|---------------------|---------------------------|---------------|-------------|
| DG 32:0 \[-16:0\]   | DG 16:0_16:0              | 586.5         | 313.3       |
| DG 36:1 \[NL-18:1\] | DG 18:1_18:0              | 640.6         | 341.3       |
| TG 54:3 \[-18:1\]   | TG 18:1_36:2              | 902.8         | 603.5       |
| TG 54:3 \[NL-18:2\] | TG 18:2_36:1              | 902.8         | 605.5       |

Just to recall, these transition names measure the amount of fatty acyl chain attached to the given DG or TG. For example, TG 54:3 [NL-18:1] measures the amount of fatty acyl chain 18:1 attached to TG 54:3 while TG 54:3 [-18:2] measures the amount of fatty acyl chain 18:2 attached to TG 54:3 instead.

In general, they are in the form 
- {acyl_class} {total_C}:{total_DB} [NL-{measured_C}:{measured_DB}]. 

We need to transform into the form

- {acyl_class} {measured_C}:{measured_DB}\_{remaining_C}:{remaining_DB} 

where

- {remaining_C} is {total_C - measured_C}
- {remaining_DB} is {total_DB - measured_DB}

## R packages used

```{r message=FALSE}
library("rgoslin")
library("reactable")
library("flair")
library("here")
library("readxl")
library("magrittr")
library("stringr")
library("dplyr")
library("purrr")
library("report")
```

## The plan

We recall the following steps needed to clean such transition names.

-   Get the acyl class of the transition. {acyl_class}

-   Get the total carbon number of the transition. {total_C}

-   Get the total number of double bond of the transition {total_DB}

-   Get the total carbon number of the measured fatty acid chain. {measured_C}

-   Get the total number of double bond of the measured fatty acid chain. {measured_DB}

-   Use the tools above to clean the transition name.

## Read data

```{r read_data, warning=FALSE, message=FALSE}
annotation_data <- readxl::read_excel(
  path = here::here("content", 
                    "blog",
                    "2022-04-23-Clean-Lipid-Names-3",
                    "Annotation.xlsx"),
  sheet = "Transition_Name_Annot"
  )

reactable::reactable(annotation_data, defaultPageSize = 5)
```

## Get the acyl class {acyl_class}

We now try to get {acyl_class} from {acyl_class} {total_C}:{total_DB} [NL-{measured_C}:{measured_DB}].

To extract the (DG or DAG) or (TG or TAG) in the front of the transition name, we first add the `^` to indicate the software to look at the beginning of the string. Next, as the first letter can only be a D or T, we use the pattern `[D|T]`. Recall that `|` means or. As A is optional (appear zero or one time), we add a `?` add the end of the pattern `A`. Finally we simply add the G at the end.

This gives the final pattern to be `^[D|T]A?G`

```{r message=FALSE, echo = FALSE, results = FALSE}
acyl_class <- "TG 54:3 [NL-18:1]" %>%
    stringr::str_extract(pattern = "^[D|T]A?G")

acyl_class
```

```{r get_acyl_class, message=FALSE, include = FALSE}
acyl_class <- "TG 54:3 [NL-18:1]" %>%
    stringr::str_extract(pattern = "^[D|T]A?G")

acyl_class
```

```{r, echo = FALSE}
flair::decorate("get_acyl_class") %>% 
  # flair::flair('pattern = "^',
    flair::flair('pattern = "^[D|T]A?G"',
               background = "#d2f8d2") %>% 
  flair::knit_print.with_flair()
```

## Get the total carbon number of the transition {total_C}

The next step is to extract the total carbon number of the given transition or to get {total_C} from {acyl_class} {total_C}:{total_DB} [NL-{measured_C}:{measured_DB}]. In the case of TG 54:3 [NL-18:1], the total carbon number to 54. The key is to remove the {acyl_class} on the front first and then extract the total carbon.

To do this, we will need to make use of the {acyl_class} extracted earlier as a pattern and remove them using [`stringr::str_remove`](https://stringr.tidyverse.org/reference/str_remove.html).

For me, I use [`stringr::str_glue`](https://stringr.tidyverse.org/reference/str_glue.html) to achieve this pattern. `\\s*` is just a pattern to find white spaces and remove them.

```{r message=FALSE, echo = FALSE, results = FALSE}
total_C_step_1 <- "TG 54:3 [NL-18:1]" %>%
    stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*"))

total_C_step_1
```

```{r total_C_step_1, message=FALSE, include = FALSE}
total_C_step_1 <- "TG 54:3 [NL-18:1]" %>%
    stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*"))

total_C_step_1
```

```{r, echo = FALSE}
flair::decorate("total_C_step_1") %>% 
    flair::flair('pattern = stringr::str_glue("{acyl_class}\\\\s*")',
                 background = "#d2f8d2") %>% 
  flair::knit_print.with_flair()
```

After removing the {acyl_class} on the front, we will extract the pattern {total_C}:{total_DB} with using the pattern `^\\d+:\\d+`. This works when the digits are the first character of the string. Remember that `^` tells the software to look at the start of the string.

```{r message=FALSE, echo = FALSE, results = FALSE}
total_C_step_2 <- "TG 54:3 [NL-18:1]" %>%
    stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
    stringr::str_extract(pattern = "^\\d+:\\d+")

total_C_step_2
```

```{r total_C_step_2, message=FALSE, include = FALSE}
total_C_step_2 <- "TG 54:3 [NL-18:1]" %>%
    stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
    stringr::str_extract(pattern = "^\\d+:\\d+")

total_C_step_2
```

```{r, echo = FALSE}
flair::decorate("total_C_step_2") %>% 
    flair::flair('pattern = "^\\\\d+:\\\\d+"',
                 background = "#d2f8d2") %>% 
  flair::knit_print.with_flair()
```

From {total_C}:{total_DB}, we can then extract {total_C} using the pattern `^\\d+`

```{r message=FALSE, echo = FALSE, results = FALSE}
total_C <- "TG 54:3 [NL-18:1]" %>%
    stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
    stringr::str_extract(pattern = "^\\d+:\\d+") %>%
    stringr::str_extract(pattern = "^\\d+")

total_C
```

```{r total_C, message=FALSE, include = FALSE}
total_C <- "TG 54:3 [NL-18:1]" %>%
    stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
    stringr::str_extract(pattern = "^\\d+:\\d+") %>%
    stringr::str_extract(pattern = "^\\d+")

total_C
```

```{r, echo = FALSE}
flair::decorate("total_C") %>% 
    flair::flair('pattern = "^\\\\d+"',
                 background = "#d2f8d2") %>% 
  flair::knit_print.with_flair()
```

## Get the total number of double bond of the transition {total_DB}

The next step is to extract the total double bond number of the given transition or to get {total_DB} from {acyl_class} {total_C}:{total_DB} [NL-{measured_C}:{measured_DB}]. In the case of TG 54:3 [NL-18:1], the total number of double bonds is 3.

The extraction process is similar to the previous task. The only difference is that during the stage when we have obtained {total_C}:{total_DB}, we can extract {total_DB} using the pattern `\\d+$` instead. Recall that `$` tells the software to look at the end of the string.

```{r message=FALSE, echo = FALSE, results = FALSE}
total_DB <- "TG 54:3 [NL-18:1]" %>%
    stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
    stringr::str_extract(pattern = "^\\d+:\\d+") %>%
    stringr::str_extract(pattern = "\\d+$")

total_DB
```

```{r total_DB, message=FALSE, include = FALSE}
total_DB <- "TG 54:3 [NL-18:1]" %>%
    stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
    stringr::str_extract(pattern = "^\\d+:\\d+") %>%
    stringr::str_extract(pattern = "\\d+$")

total_DB
```

```{r, echo = FALSE}
flair::decorate("total_DB") %>% 
    flair::flair('pattern = "\\\\d+$"',
                 background = "#d2f8d2") %>% 
  flair::knit_print.with_flair()
```

## Get the total carbon number of the measured fatty acid chain {measured_C}

We now try to get {measured_C} from {acyl_class} {total_C}:{total_DB} [NL-{measured_C}:{measured_DB}]. To do this, first, we again remove the acyl class on the front, giving us {total_C}:{total_DB} [NL-{measured_C}:{measured_DB}]. In the case of TG 54:3 [NL-18:1], the total number of measured carbon bonds is 18.

```{r message=FALSE, echo = FALSE, results = FALSE}
measured_C_step1 <- "TG 54:3 [NL-18:1]" %>%
  stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*"))
  
measured_C_step1
```

```{r measured_C_step1, message=FALSE, include = FALSE}
measured_C_step1 <- "TG 54:3 [NL-18:1]" %>%
  stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*"))
  
measured_C_step1
```

```{r, echo = FALSE}
flair::decorate("measured_C_step1") %>% 
    flair::flair('pattern = stringr::str_glue("{acyl_class}\\\\s*")',
                 background = "#d2f8d2") %>% 
  flair::knit_print.with_flair()
```

As the measured fatty acid chain comes with a `-`, we extract -{measured_C}:{measured_DB} from {total_C}:{total_DB} [NL-{measured_C}:{measured_DB}]. This is done by using the pattern `-\\s*\\d+:\\d+`

```{r message=FALSE, echo = FALSE, results = FALSE}
measured_C_step2 <- "TG 54:3 [NL-18:1]" %>%
  stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
  stringr::str_extract(pattern = "-\\s*\\d+:\\d+")
  
measured_C_step2
```

```{r measured_C_step2, message=FALSE, include = FALSE}
measured_C_step2 <- "TG 54:3 [NL-18:1]" %>%
  stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
  stringr::str_extract(pattern = "-\\s*\\d+:\\d+")
  
measured_C_step2
```

```{r, echo = FALSE}
flair::decorate("measured_C_step2") %>% 
    flair::flair('pattern = "-\\\\s*\\\\d+:\\\\d+"',
                 background = "#d2f8d2") %>% 
  flair::knit_print.with_flair()
```

We proceed to remove the `-` from -{measured_C}:{measured_DB}, giving us {measured_C}:{measured_DB}

```{r message=FALSE, echo = FALSE, results = FALSE}
measured_C_step3 <- "TG 54:3 [NL-18:1]" %>%
  stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
  stringr::str_extract(pattern = "-\\s*\\d+:\\d+") %>%
  stringr::str_remove(pattern = "-")
  
measured_C_step3
```

```{r measured_C_step3, message=FALSE, include = FALSE}
measured_C_step3 <- "TG 54:3 [NL-18:1]" %>%
  stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
  stringr::str_extract(pattern = "-\\s*\\d+:\\d+") %>%
  stringr::str_remove(pattern = "-")
  
measured_C_step3
```

```{r, echo = FALSE}
flair::decorate("measured_C_step3") %>% 
    flair::flair('pattern = "-"',
                 background = "#d2f8d2") %>% 
  flair::knit_print.with_flair()
```

Finally, we again use the pattern `^\\d+` to extract the {measured_C}

```{r message=FALSE, echo = FALSE, results = FALSE}
measured_C <- "TG 54:3 [NL-18:1]" %>%
  stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
  stringr::str_extract(pattern = "-\\s*\\d+:\\d+") %>%
  stringr::str_remove(pattern = "-") %>%
  stringr::str_extract(pattern = "^\\d+")

measured_C
```

```{r measured_C, message=FALSE, include = FALSE}
measured_C <- "TG 54:3 [NL-18:1]" %>%
  stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
  stringr::str_extract(pattern = "-\\s*\\d+:\\d+") %>%
  stringr::str_remove(pattern = "-") %>%
  stringr::str_extract(pattern = "^\\d+")

measured_C
```

```{r, echo = FALSE}
flair::decorate("measured_C") %>% 
    flair::flair('pattern = "^\\\\d+"',
                 background = "#d2f8d2") %>% 
  flair::knit_print.with_flair()
```

## Get the total number of double bond of the measured fatty acid chain {measured_DB}

We now try to get {measured_DB} from {acyl_class} {total_C}:{total_DB} [NL-{measured_C}:{measured_DB}]. In the case of TG 54:3 [NL-18:1], the total number of measured double bonds is 1.

The process is similar to the previous section, the difference is that during the stage when we have obtained {measured_C}:{measured_DB}, we can extract {measured_DB} using the pattern `\\d+$` instead.

```{r message=FALSE, echo = FALSE, results = FALSE}
measured_DB <- "TG 54:3 [NL-18:1]" %>%
    stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
    stringr::str_extract(pattern = "-\\s*\\d+:\\d+") %>%
    stringr::str_remove(pattern = "-") %>%
    stringr::str_extract(pattern = "\\d+$")

measured_DB 
```

```{r measured_DB, message=FALSE, include = FALSE}
measured_DB <- "TG 54:3 [NL-18:1]" %>%
    stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
    stringr::str_extract(pattern = "-\\s*\\d+:\\d+") %>%
    stringr::str_remove(pattern = "-") %>%
    stringr::str_extract(pattern = "\\d+$")

measured_DB 
```

```{r, echo = FALSE}
flair::decorate("measured_DB") %>% 
    flair::flair('pattern = "\\\\d+$"',
                 background = "#d2f8d2") %>% 
  flair::knit_print.with_flair()
```

## Check if extraction is successful

There will be situation when the extraction will fail due to a new input of transitions that the function has not encountered before. To check for this issue, we have the following.

```{r message=FALSE, echo = FALSE, results = FALSE}
input_acyl <- "TG 54:3 [NL-18:1]"

if (!isTRUE(stringr::str_detect(total_C, "^[0-9]+$"))) {
  stop(glue::glue("Extracting total carbon in {input_acyl} has failed"))
}

if (!isTRUE(stringr::str_detect(total_DB, "^[0-9]+$"))) {
  stop(glue::glue("Extracting total double bond in {input_acyl} has failed"))
}

if (!isTRUE(stringr::str_detect(measured_C, "^[0-9]+$"))) {
  stop(glue::glue("Extracting measured carbon in {input_acyl} has failed"))
}

if (!isTRUE(stringr::str_detect(measured_DB, "^[0-9]+$"))) {
  stop(glue::glue("Extracting measured double bond in {input_acyl} has failed"))
}
```

```{r check_extraction, message=FALSE, include = FALSE}
input_acyl <- "TG 54:3 [NL-18:1]"

if (!isTRUE(stringr::str_detect(total_C, "^[0-9]+$"))) {
  stop(glue::glue("Extracting total carbon in {input_acyl} has failed"))
}

if (!isTRUE(stringr::str_detect(total_DB, "^[0-9]+$"))) {
  stop(glue::glue("Extracting total double bond in {input_acyl} has failed"))
}

if (!isTRUE(stringr::str_detect(measured_C, "^[0-9]+$"))) {
  stop(glue::glue("Extracting measured carbon in {input_acyl} has failed"))
}

if (!isTRUE(stringr::str_detect(measured_DB, "^[0-9]+$"))) {
  stop(glue::glue("Extracting measured double bond in {input_acyl} has failed"))
}
```

```{r, echo = FALSE}
flair::decorate("check_extraction") %>% 
    flair::flair('"^[0-9]+$"',
                 background = "#d2f8d2") %>%
    flair::flair('isTRUE',
                 background = "#d2f8d2") %>% 
  flair::knit_print.with_flair()
```

The pattern `^[0-9]+$` means the software will try to detect digits 0 to 9 (indicated by `[0-9]`). The digits can appear one or more times (indicated by `+`) and the start (indicated by `^`) and the end (indicated by `$`) of the string must contain only these digits.

The reason we use `isTRUE` is to ensure that only logicals `TRUE` and `FALSE` are returned. It is possible for `stringr::str_detect` to return `NA`. Take a look at this [Win Vector LLC blog post](https://win-vector.com/2018/06/11/r-tip-use-istrue) for more information.

## Use the tools above to clean the transition name

With the {acyl_class}, {total_C}, {total_DB}, {measured_C} and {measured_DB} extracted successfully, we can proceed to calculate

-   {remaining_C} as {total_C - measured_C}
-   {remaining_DB} as {total_DB - measured_DB}

```{r message=FALSE}
remaining_C <- (as.numeric(total_C) - as.numeric(measured_C)) %>%
    as.character()

remaining_C
```

```{r message=FALSE}
remaining_DB <- (as.numeric(total_DB) - as.numeric(measured_DB)) %>%
  as.character()

remaining_DB
```

Lastly, we use [`stringr::str_glue`](https://stringr.tidyverse.org/reference/str_glue.html) to construct {acyl_class} {measured_C}:{measured_DB}\_{remaining_C}:{remaining_DB}

```{r message=FALSE}
clean_acyl <- stringr::str_glue(
    "{acyl_class} {measured_C}:{measured_DB}_{remaining_C}:{remaining_DB}"
  ) %>%
    as.character()

clean_acyl
```

## Putting it all together

Combining what we have accomplished from the previous and this section, we have the following function and corresponding documentation.

```{r message=FALSE}
#' @title Clean Acyl Lipids
#' @description Clean Acyl Lipids for `rgoslin` input
#' @param input_acyl A character string highlighting a lipid,
#' Default: 'DG 30:0 \[NL-15:0\]'
#' @return A acyl lipid that `rgoslin` can accept
#' @details We only accept DG, DAG, TG, TAG for now.
#' Input Acyl Lipid is of the form
#' {acyl_class} {total_C}:{total_DB} \[NL-{measured_C}:{measured_DB}\]
#' where C is carbon and DB is double bond
#' Output Acyl Lipid is of the form
#' {acyl_class} {measured_C}:{measured_DB}_{remaining_C}:{remaining_DB}
#' where {remaining_C} is {total_C - measured_C}
#' and {remaining_DB} is {total_DB - measured_DB}
#' @examples
#' clean_acyl(input_acyl = "DG 32:0 [-16:0]")
#' @rdname clean_acyl
#' @export
clean_acyl <- function(input_acyl = "DG 32:0 [NL-16:0]") {

  # If we have a sum composition labelled as [SIM] at the end
  # after removing the (a\b) and (ISTD)
  if(isTRUE(stringr::str_detect(string = input_acyl,
                         pattern = "\\s*\\[SIM\\]\\s*$"))) {

    input_acyl <- input_acyl %>%
      stringr::str_remove(pattern = "\\s*\\[SIM\\]\\s*$")

    return(input_acyl)

  }

  # If we have no neutral loss labeling
  if(!isTRUE(stringr::str_detect(string = input_acyl,
                                pattern = "\\s*(\\[)?(NL)?-\\s*\\d+:\\d+(\\])?\\s*$"))) {

    return(input_acyl)

  }

  # From here all should end with [NL-XX:X]

  acyl_class <- input_acyl %>%
    stringr::str_extract(pattern = "^[D|T]A?G")

  total_C <- input_acyl %>%
    stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
    stringr::str_extract(pattern = "^\\d+:\\d+") %>%
    stringr::str_extract(pattern = "^\\d+")

  total_DB <- input_acyl %>%
    stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
    stringr::str_extract(pattern = "^\\d+:\\d+") %>%
    stringr::str_extract(pattern = "\\d+$")

  measured_C <- input_acyl %>%
    stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
    stringr::str_extract(pattern = "-\\s*\\d+:\\d+") %>%
    stringr::str_remove(pattern = "-") %>%
    stringr::str_extract(pattern = "^\\d+")

  measured_DB <- input_acyl %>%
    stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
    stringr::str_extract(pattern = "-\\s*\\d+:\\d+") %>%
    stringr::str_remove(pattern = "-") %>%
    stringr::str_extract(pattern = "\\d+$")

  if(!isTRUE(stringr::str_detect(total_C, "^[0-9]+$"))) {
    stop(glue::glue("Extracting total carbon in {input_acyl} has failed"))
  }

  if(!isTRUE(stringr::str_detect(total_DB, "^[0-9]+$"))) {
    stop(glue::glue("Extracting total double bond in {input_acyl} has failed"))
  }

  if(!isTRUE(stringr::str_detect(measured_C, "^[0-9]+$"))) {
    stop(glue::glue("Extracting measured carbon in {input_acyl} has failed"))
  }

  if(!isTRUE(stringr::str_detect(measured_DB, "^[0-9]+$"))) {
    stop(glue::glue("Extracting measured double bond in {input_acyl} has failed"))
  }

  remaining_C <- (as.numeric(total_C) - as.numeric(measured_C)) %>%
    as.character()

  remaining_DB <- (as.numeric(total_DB) - as.numeric(measured_DB)) %>%
    as.character()

  output_acyl <- stringr::str_glue(
    "{acyl_class} {measured_C}:{measured_DB}_{remaining_C}:{remaining_DB}"
  ) %>%
    as.character()

  return(output_acyl)

}
```

## Plan execution

Here is how it looks like when the function is utilised.

```{r plan_execution, warning=FALSE, message=FALSE}

cleaned_data <- annotation_data %>% 
  dplyr::mutate(
    `Clean Name For Annotation` = purrr::map(.data[["Given Name"]],
                                             clean_acyl
                                             ) )%>% 
  # Make Given Name and Clean Name the first two columns
  dplyr::relocate(
    dplyr::any_of(c("Given Name","Clean Name For Annotation"))
    ) 

cleaned_data %>%
  reactable::reactable(defaultPageSize = 5)

```

```{r}
cleaned_data[["Clean Name For Annotation"]] %>% 
  rgoslin::parseLipidNames() %>%
  reactable::reactable(defaultPageSize = 5)
```

## Package references

```{r warning=FALSE, message=TRUE, results='asis'}

get_citation <- function(package_name) {
  transform_name <- package_name %>% 
    citation() %>% 
    format(style="text")
  return(transform_name)
} 

packages <- c("base","rgoslin", "reactable", "flair",
              "here", "readxl", "magrittr",
              "stringr", "dplyr", "report", "purrr")

table <- tibble::tibble(Packages = packages)

table %>%
  dplyr::mutate(
    transform_name = purrr::map_chr(.data[["Packages"]],
                                    get_citation)
  ) %>% 
  dplyr::pull(.data[["transform_name"]]) %>% 
  report::as.report_parameters()

```
