---
title: "Cleaning Lipid Names for Annotation Part 3"
subtitle: ""
excerpt: "This post provides some tips on how to clean lipid names input suited for some current nomenclature tools using R"
date: 2022-03-07
author: "Jeremy Selva"
draft: true
images:
series:
tags:
categories:
output: md_document #needed for flair to work
layout: single-sidebar
bibliography: utils/bibliography.bib
csl: utils/f1000research.csl
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(fig.align = "center")

```

## Introduction

In this blog, I will introduce another set of lipid annotations that my workplace uses that require to be cleaned up and modified so that they can be processed by lipid annotations converter tools like [Goslin](https://lifs-tools.org/goslin) [@GOSLIN] and [RefMet](https://metabolomicsworkbench.org/databases/refmet/index.php) [@Fahy2020].

## R Packages Used

```{r message=FALSE}
library("rgoslin")
library("reactable")
library("flair")
library("here")
library("readxl")
library("magrittr")
library("stringr")
library("dplyr")
library("report")
```

## Labels to clean

Putting it all together, we have the following function and corresponding documentation.

```{r message=FALSE}
#' @title Clean Acyl Lipids
#' @description Clean Acyl Lipids for `rgoslin` input
#' @param input_acyl A character string highlighting a lipid,
#' Default: 'DG 30:0 \[NL-15:0\]'
#' @return A acyl lipid that `rgoslin` can accept
#' @details We only accept DG, DAG, TG, TAG for now.
#' Input Acyl Lipid is of the form
#' {acyl_class} {total_C}:{total_DB} \[NL-{measured_C}:{measured_DB}\]
#' where C is carbon and DB is double bond
#' Output Acyl Lipid is of the form
#' {acyl_class} {measured_C}:{measured_DB}_{remaining_C}:{remaining_DB}
#' where {remaining_C} is {total_C - measured_C}
#' and {remaining_DB} is {total_DB - measured_DB}
#' @examples
#' clean_acyl_dynamo(input_acyl = "DG 32:0 [-16:0]")
#' @rdname clean_acyl
#' @export
clean_acyl <- function(input_acyl = "DG 32:0 [NL-16:0]") {

  # If we have a sum composition labelled as [SIM] at the end
  # after removing the (a\b) and (ISTD)
  if(isTRUE(stringr::str_detect(string = input_acyl,
                         pattern = "\\s*\\[SIM\\]\\s*$"))) {

    input_acyl <- input_acyl %>%
      stringr::str_remove(pattern = "\\s*\\[SIM\\]\\s*$")

    return(input_acyl)

  }

  # If we have no neutral loss labeling
  if(!isTRUE(stringr::str_detect(string = input_acyl,
                                pattern = "\\s*(\\[)?(NL)?-\\s*\\d+:\\d+(\\])?\\s*$"))) {

    return(input_acyl)

  }

  # From here all should end with [NL-XX:X]

  acyl_class <- input_acyl %>%
    stringr::str_extract(pattern = "^[D|T]A?G")

  total_C <- input_acyl %>%
    stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
    stringr::str_extract(pattern = "^\\d+:\\d+") %>%
    stringr::str_extract(pattern = "^\\d+")

  total_DB <- input_acyl %>%
    stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
    stringr::str_extract(pattern = "^\\d+:\\d+") %>%
    stringr::str_extract(pattern = "\\d+$")

  measured_C <- input_acyl %>%
    stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
    stringr::str_extract(pattern = "-\\s*\\d+:\\d+") %>%
    stringr::str_remove(pattern = "-") %>%
    stringr::str_extract(pattern = "^\\d+")

  measured_DB <- input_acyl %>%
    stringr::str_remove(pattern = stringr::str_glue("{acyl_class}\\s*")) %>%
    stringr::str_extract(pattern = "-\\s*\\d+:\\d+") %>%
    stringr::str_remove(pattern = "-") %>%
    stringr::str_extract(pattern = "\\d+$")

  if(!isTRUE(stringr::str_detect(total_C, "^[0-9]+$"))) {
    stop(glue::glue("Extracting total carbon in {input_acyl} has failed"))
  }

  if(!isTRUE(stringr::str_detect(total_DB, "^[0-9]+$"))) {
    stop(glue::glue("Extracting total double bond in {input_acyl} has failed"))
  }

  if(!isTRUE(stringr::str_detect(measured_C, "^[0-9]+$"))) {
    stop(glue::glue("Extracting measured carbon in {input_acyl} has failed"))
  }

  if(!isTRUE(stringr::str_detect(measured_DB, "^[0-9]+$"))) {
    stop(glue::glue("Extracting measured double bond in {input_acyl} has failed"))
  }

  remaining_C <- (as.numeric(total_C) - as.numeric(measured_C)) %>%
    as.character()

  remaining_DB <- (as.numeric(total_DB) - as.numeric(measured_DB)) %>%
    as.character()

  clean_acyl <- stringr::str_glue(
    "{acyl_class} {measured_C}:{measured_DB}_{remaining_C}:{remaining_DB}"
  ) %>%
    as.character()

  return(clean_acyl)

}
```

## Package References

```{r warning=FALSE, message=TRUE, results='asis'}
report::cite_packages(sessionInfo())
```

## References
